Clicks and Cliques

### 2018-12-18 papersoul.Rnw
use tidy code for census data

<<data,echo=FALSE,warning=FALSE,message=FALSE, cache=FALSE>>=
# Procesing data sets from SOCT and Census Bureau
source('code/data_chk_tidy.R')
source('code/census_chk.R')
# loading results from cluster and random forest models.

@@

# Compute comunity proportion of attached people
lev <- soul %>% pull(QSB) %>% levels()
census.data %<>%
        mutate(QSB = factor(census.data$QSB, labels = sort(lev))) %>%
        left_join(att.pr[, c("QSB", "CCEGRP2Attached", "CCEGRP2Not Attached")], by = "QSB") %>% 
        mutate(QSB = reorder(QSB, CCEGRP2Attached))

@@

aux.mer <- merge(lon.lat, census.data[, c(1, 7)], by.x = 'Community', by.y = 'QSB')
aux.mer$cate[aux.mer$pop100 < 3] <- 1
aux.mer$cate[aux.mer$pop100 >= 3&aux.mer$pop100 < 8] <- 2
aux.mer$cate[aux.mer$pop100 >= 8 & aux.mer$pop100 < 20] <- 3
aux.mer$cate[aux.mer$pop100 >= 20] <- 4

@@

\begin{figure}[hbpt]
<<corplot, echo=FALSE, dependson=c('data'),cache=TRUE>>=
# With Census data we want to describe communities
cors1 <- cor(x = census.data[, 2:63], y = census.data[, 64])
cors2 <- cor(x = census.data[, 2:63], y = census.data[, 65])

nm <- names(cors1[ rank(cors1) %in% c(1:10, 53:62), ])

dat.cor <- rbind(
data.frame(vars = rownames(cors1), cor = cors1[,1], positive = cors1[,1]>0, type = 'Attached') ,
data.frame(vars = rownames(cors2), cor = cors2[,1], positive = cors2[,1]>0, type = 'Not Attached') )

dat.cor2 <- subset(dat.cor, vars %in% nm)
dat.cor2$vars <- reorder(factor(dat.cor2$vars), (dat.cor2$cor) *(dat.cor2$type=='Attached'), mean)

@@

qplot(data = dat.cor2, y = vars, x = cor, xlab = 'Correlation', ylab = '', color = positive, facets =~type, size = I(3)) + theme(legend.position= 'bottom', legend.title = element_blank(), axis.text.y = element_text(size = I(15)))
@
\caption{Correlations with attached and not attached proportion in order from top to bottom based on correlation with attached\label{corplot}. This plot shows the 10 more relevant variables with positive correlation and 10 with negative correlation with attachment.}
\end{figure}

>>>>

<<data,echo=FALSE,warning=FALSE,message=FALSE, cache=FALSE>>=
# Procesing data sets from SOCT and Census Bureau
source('code/data_chk_tidy.R')
source('code/census_chk_tidy.R')
# loading results from cluster and random forest models.

@@

# Compute comunity proportion of attached people
# community labels differ from soul and census datasets

lev <- soul %>% pull(QSB) %>% levels()
census.data %<>%
        mutate(QSB = factor(QSB, labels = sort(lev))) %>%
        left_join(att.pr[, c("QSB", "CCEGRP2Attached", "CCEGRP2Not Attached")], by = "QSB") %>% 
        mutate(QSB = reorder(QSB, CCEGRP2Attached))

@@

aux.mer <- inner_join(lon.lat, 
                 select(census.data.new, QSB,pop100), 
                 by = c('Community'='QSB') )

aux.mer$cate[aux.mer$pop100 < 3] <- 1
aux.mer$cate[aux.mer$pop100 >= 3&aux.mer$pop100 < 8] <- 2
aux.mer$cate[aux.mer$pop100 >= 8 & aux.mer$pop100 < 20] <- 3
aux.mer$cate[aux.mer$pop100 >= 20] <- 4

@@

\begin{figure}[hbpt]
<<corplot, echo=FALSE, dependson=c('data'),cache=TRUE>>=
# With Census data we want to describe communities

# cors1 <- cor(x = census.data[, 2:63], y = census.data[, 64])
# cors2 <- cor(x = census.data[, 2:63], y = census.data[, 65])
# nm <- names(cors1[ rank(cors1) %in% c(1:10, 53:62), ])
# dat.cor <- rbind(
# data.frame(vars = rownames(cors1), cor = cors1[,1], positive = cors1[,1]>0, type = 'Attached') ,
# data.frame(vars = rownames(cors2), cor = cors2[,1], positive = cors2[,1]>0, type = 'Not Attached') )
# dat.cor2 <- subset(dat.cor, vars %in% nm)
# dat.cor2$vars <- reorder(factor(dat.cor2$vars), (dat.cor2$cor) *(dat.cor2$type=='Attached'), mean)

cors <- census.data.new %>% 
  gather(vars, vv, -QSB, -CCEGRP2Attached, -`CCEGRP2Not Attached` ) %>%
  group_by(vars) %>% 
  summarise(
    cor.att = cor(vv, CCEGRP2Attached, use = 'complete.obs'),
    cor.noatt = cor(vv, `CCEGRP2Not Attached`, use = 'complete.obs') ) %>% 
  filter(!is.na(cor.att), vars != 'unemployed') %>% 
  filter(rank(cor.att) %in% c(1:10, 52:61) ) %>% 
  mutate(vars =  fct_reorder(vars, cor.att) ) %>% 
  gather(type, vv, -vars) %>% 
  mutate( type = factor(type, labels=c('Attached', 'Not Attached') ),
          positive = factor(sign(vv), labels=c( 'Negative', 'Positive') ) )

@@

qplot(data = dat.cor2, y = vars, x = cor, xlab = 'Correlation', ylab = '', color = positive, facets =~type, size = I(3)) + theme(legend.position= 'bottom', legend.title = element_blank(), axis.text.y = element_text(size = I(15)))

# cors %>% 
#   ggplot() + 
#   geom_point(aes(y = vars, x=vv, color = positive)) +
#   facet_grid(~type)

@
\caption{Correlations with attached and not attached proportion in order from top to bottom based on correlation with attached\label{corplot}. This plot shows the 10 more relevant variables with positive correlation and 10 with negative correlation with attachment.}
\end{figure}
